### 2014-01-14 machine-learning/cifar-project/report/report.tex
mod reports

\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}
\usepackage{tocloft}

@@

	\subsection{About Makarovski}
		Well I think that you should notice Makarovski.
		{\color{red}TODO: Mention some junk!}

@@

	\subsection{K-Means Clustering}
		{\color{red}TODO: Mention classical K-Means algorithm!}

@@

	\subsection{SVM Classifier}
		{\color{red}TODO: Mention some junk!}

@@

\section{Conclusion}
		{\color{red}TODO: Mention some junk!}

>>>>

\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
%\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}
\usepackage{tocloft}

@@

	%\subsection{About Makarovski}
		%Well I think that you should notice Makarovski.
		%{\color{red}TODO: Mention some junk!}

@@

	\subsection{K-Means Clustering}
		K-means clustering is a method of vector quantization, originally from signal processing, that is popular for cluster analysis in data mining. k-means
        clustering aims to partition n observations into k clusters in which each observation belongs to the cluster with the nearest mean, serving as a prototype of the cluster.

@@

	\subsection{SVM Classifier}
		In machine learning, support vector machines (SVMs, also support vector networks) are supervised learning models with associated learning algorithms
        that analyze data and recognize patterns, used for classification and regression analysis. Given a set of training examples, each marked as belonging to one of two categories, an SVM training algorithm builds a model that assigns new examples into one category or the other, making it a non-probabilistic binary linear classifier.

@@

%\section{Conclusion}
		%{\color{red}TODO: Mention some junk!}
